---
title: "Assignment 1"
---

# Assignment 1

My first assignment has two parts.

## (a) Choose a video from one of the following sources and provide a brief summary in your Quarto document:

I chose "Veri Bilimi ve Endüstri Mühendisliği Üzerine Sohbetler -Kerem Demirtaş & Erdi Daşdemir" because Kerem Demirtaş is from Adana like me.

He discusses how large companies such as McKinsey, Tesla, RELEX, and Blue Yonder use data analysis to solve problems in areas like retail, healthcare, and transportation. After this introduction, he explains “what data science is not” and addresses several common misconceptions about the field. He then presents the typical data science workflow, which consists of six steps, and describes each step by referring to how similar processes were carried out historically before and after computers became widely integrated into daily life. After completing the discussion on data science, he introduces his thesis topic titled “An Object-Driven Cellular Automaton Model for Platooning of Autonomous Vehicles in Mixed Traffic on Freeways with Multiple Lanes.” The main motivation of this work is to reduce the following distance between autonomous vehicles by enabling convoying (platooning) behavior in traffic, thereby improving traffic efficiency and flow.

Open Ended Question:
In 1997, the chess computer Deep Blue, developed by IBM, defeated world chess champion Garry Kasparov in a historic match. Deep Blue relied on searching millions of chess positions per second and evaluating positions using a large set of hand-crafted evaluation parameters.

From a machine learning perspective, consider the concepts of underfitting, overfitting, and well-balanced generalization. Do you think Deep Blue’s decision algorithm is closer to underfitting, overfitting, or a well-balanced model? Explain your reasoning by discussing how Deep Blue evaluates chess positions and why its approach fits the category you selected.
Answer: Deep Blue’s behavior can be interpreted as overfitting.

Overfitting occurs when a model performs very well on patterns it is optimized for, but its performance decreases when it encounters unexpected or different situations. In the Kasparov–Deep Blue matches, some analysts argued that Deep Blue was extremely strong in positions and patterns that were well represented in its evaluation function and search heuristics. However, when Kasparov changed his strategy and played unusual or unconventional moves, Deep Blue sometimes struggled. This suggests that Deep Blue’s algorithm relied heavily on specific evaluation rules and patterns designed by chess experts. When the game moved outside these expected structures, the system could become less effective. In other words, it was very powerful within the domain it was optimized for but less adaptable to novel strategies.

Multiple Choice Question:
Which one is not a step in Typical Data Science Workflow?
A)Problem Definition(Formulation) <br>
B)Data Collection and Preparation <br>
C)Model Building and Algorithms <br>
D)Production(Action) and Live Performance <br>
E)Prediction Generation Without Model  Training<br>

Answer: E


## (b)Complete the following tasks. Be sure to include the R code used to generate these outputs.
Import the polls_us_election_2016 data set from the dslabs package
```{r}
#install.packages("dslabs")
```
I opened the dslabs with the library command in my script.
```{r}
library(dslabs)
```

